\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-31 OaklandSubmission/pipe.tex
nit
why this no end

Thus, given a decomposition of $\prog$ into
$\prog_1\seq\prog_2\seq\dots\seq\prog_k$, we can use the construction
above to generate programs $\progn_1,\progn_2,\ldots,\progn_k$, that
can be sequentially executed, using the unmodified underlying \mpc
backend. The following theorem state the correctness and security of
the scheme.

\begin{theorem}[Correctness and security of partitioning]
If $\prog_1||\prog_2||\ldots||\prog_k$ is a decomposition of a program $\prog$, then there exists a sequence of programs $\progn_1, \progn_2, \ldots, \progn_k$ and protocols $\prot_1, \prot_2, \ldots, \prot_k$ such that for all $i$, $\prot_i$ securely realizes $\progn_i$ and  $\prot
= \prot_1\seq\prot_2\dots\seq\prot_k$ securely realizes $s$.
\end{theorem}

\noindent {\em Proof.} Let $\progn_1, \ldots, \progn_k$ be the
sequence of programs as defined above corresponding to the
decomposition $\prog = \prog_1||\prog_2||\ldots||\prog_k$.  For every
$1\leq i\leq k$, let $\prot_i$ be the \mpc protocol output by our
framework for $\progn_i$. Our construction for programs $\progn_i$
ensures that if $\prog$ is well-typed, then for each $1\leq i \leq k$,
$\progn_i$ is well-typed. Then, by \theoremref{security}, $\prot_i$
securely realizes $\progn_i$. That is, for every $1\leq i \leq k-1$,
the protocol $\prot_i$ provides observations $r_i$ to Alice and $o_i$
to Bob. And, protocol $\prot_k$ provides observation $z$ to both Alice
and Bob. Finally, since $r_i$ and $o_i$ ($1\leq i\leq k-1$) are
individually uniformly random (in $(\mathbb{Z},+)$, outputs received
by the adversary can be simulated given the final output $z$.

>>>>

Thus, given a decomposition of $\prog$ into
$\prog_1\seq\prog_2\seq\dots\seq\prog_k$, we can use the construction
above to generate programs $\progn_1,\progn_2,\ldots,\progn_k$, that
can be sequentially executed, using the unmodified underlying \mpc
backend. The following theorem states the correctness and security of
the scheme.

\begin{theorem}[Correctness and security of partitioning]
If $\prog_1||\prog_2||\ldots||\prog_k$ is a decomposition of a program $\prog$, then there exists a sequence of programs $\progn_1, \progn_2, \ldots, \progn_k$ and protocols $\prot_1, \prot_2, \ldots, \prot_k$ such that for all $i$, $\prot_i$ securely realizes $\progn_i$ and  $\prot
= \prot_1,\prot_2,\dots,\prot_k$ securely realizes $s$.
\end{theorem}

\noindent {\em Proof.} Let $\progn_1, \ldots, \progn_k$ be the
sequence of programs as defined above corresponding to the
decomposition $\prog = \prog_1||\prog_2||\ldots||\prog_k$.  For every
$1\leq i\leq k$, let $\prot_i$ be the \mpc protocol output by our
framework for $\progn_i$. Our construction for programs $\progn_i$
ensures that if $\prog$ is well-typed, then for each $1\leq i \leq k$,
$\progn_i$ is well-typed. Then, by \theoremref{security}, $\prot_i$,
the \mpc protocol that evaluates the circuit generated by $\progn_i$,
securely realizes $\progn_i$. That is, for every $1\leq i \leq k-1$,
the protocol $\prot_i$ provides observations $r_i$ to Alice and $o_i$
to Bob. And, protocol $\prot_k$ provides observation $z$ to both Alice
and Bob. Finally, since $r_i$ and $o_i$ ($1\leq i\leq k-1$) are
individually uniformly random (in $(\mathbb{Z},+)$, outputs received
by the adversary can be simulated given the final output $z$.

### 2017-10-31 OaklandSubmission/security.tex
why this no end

We shall assume a cryptographic \mpc backend that securely implements
any circuit $\crct$ that is output by our compiler
(see \figureref{circuits}). In more detail, this means that for any
well-typed source program $s$, let $\crct$ be the output circuit output
(as in \theoremref{correctness}). We assume that there
exists a \mpc protocol $\prot$ that securely realizes the
functionality $\crct$ and let $\simu_{\tiny{2pc}}$ be the
corresponding simulator  (that runs on $\crct$, input of the corrupt
party and the output obtained from trusted functionality for
$\crct$). We note that ABY~\cite{aby} provides such a protocol
$\prot$ and simulator $\simu_{\tiny{2pc}}$ for all circuits $\crct$
output in our framework. We now state and prove our
security theorem.

\begin{theorem}[Security]\label{theorem:security}
Let $s$ be any functionality or program in our source language with
outputs (or observations) $O_1$, that outputs a circuit
$\chi$ (as defined in Theorem \ref{theorem:correctness}). Let protocol
$\prot$ be the two-party secure computation protocol that securely
realizes $\chi$ (as defined above). Then, $\prot$ securely realizes
$s$.
\end{theorem}

\noindent {\em Proof.} 
Our simulator $\simu$ simply runs our compiler on program $s$ to obtain $\crct$. It is crucial that this compilation to circuits does not require the secret inputs of the parties. Next, $\simu$ sends the input of the corrupt party to the trusted functionality of $s$ to obtain outputs $O_1$. Note that $O_1$ is same as the observations in the source semantics. 
By \theoremref{correctness}, these outputs $O_1$ are identical to outputs (or observations) $O_2$ of $\crct$ under circuit semantics. 
Next, $\simu$ runs $\simu_{\tiny{2pc}}$ on $\crct$, input of the corrupt party and $O_2$. 
From the security of $\prot$, we have that the simulated view output by $\simu_{\tiny{2pc}}$ is indistinguishable from the real view of the $\prot$ for $\crct$ between the two parties. Hence, the security follows.

>>>>

We shall assume a cryptographic \mpc backend that securely implements
any circuit $\crct$ that is output by our compiler
(see \figureref{circuits}). This means that for any
well-typed source program $s$, let $\crct$ be the circuit generated
as in \theoremref{correctness}. We assume that there
exists a \mpc protocol $\prot$ that securely realizes the
functionality $\crct$ and let $\simu_{\tiny{2pc}}$ be the
corresponding simulator  (that runs on $\crct$, input of the corrupt
party and the output obtained from trusted functionality for
$\crct$). We note that ABY~\cite{aby} provides such a protocol
$\prot$ and simulator $\simu_{\tiny{2pc}}$ for all circuits $\crct$
output in our framework. We now state and prove our
security theorem.

\begin{theorem}[Security]\label{theorem:security}
Let $s$ be a well typed program in our source language
that generates a circuit
$\chi$ (as defined in Theorem \ref{theorem:correctness}). Let protocol
$\prot$ be the two-party secure computation protocol that securely
realizes $\chi$ (as defined above). Then, $\prot$ securely realizes
$s$.
\end{theorem}

\noindent {\em Proof.} 
Our simulator $\simu$ simply runs our compiler on program $s$ to obtain $\crct$. It is crucial that this compilation to circuits does not require the secret inputs of the parties. Next, $\simu$ sends the input of the corrupt party to the trusted functionality of $s$ to obtain outputs $O_1$. Note that $O_1$ is same as the observations in the source semantics. 
By \theoremref{correctness}, these outputs $O_1$ are identical to outputs (or observations) $O_2$ of $\crct$ under circuit semantics. 
Next, $\simu$ runs $\simu_{\tiny{2pc}}$ on $\crct$, input of the corrupt party and $O_2$.
% (note, while $\simu_{\tiny{2pc}}$ expects output $O_1$ as its input, it is ok for $\simu$ to run $\simu_{\tiny{2pc}}$ on $O_2$ instead as $O_2=O_1$). 
From the security of $\prot$, we have that the simulated view output by $\simu_{\tiny{2pc}}$ is indistinguishable from the real view. Hence, the security follows.
